Import and process AODV3 Level2 AOD20 from Aeronet

### 2019-07-25 Code/03_import_AOD_V3.Rmd
calc. AOD buffer variables

---
title: "Import and process AODV3 Level2 AOD20 from Aeronet"
author: "Yang Liu"
date: "6/4/2019"
output:
  html_document:
    toc: true
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, warning=FALSE,
                      error = F, fig.width = 7, fig.height = 4.5)
# error=TRUE allows error 
```

Borrowed code from `03_import_aeronet.R` on Jdrive  
Import and process the AOD20 V3 level 2 global Aeronet stations  
Interpolating to wavelength AOD 470nm

@@

```{r}
suppressPackageStartupMessages({
library(fst); library(data.table); library(ggplot2)
library(sf)
library(ggmap)
})

source("~/Jdrive/PM/Just_Lab/projects/ECHO_PM/code/liuy29/funcs_for_plots.R")
source("~/liuyanguu/ECHO_PM/code/cwv_funcs.R")

@@

aod_site_sf <- st_as_sf(site_locations_2019, coords = c("lon", "lat"), crs = 4326)
nemia_buff_aea <- readRDS("~/Jdrive/PM/Just_Lab/projects/ECHO_PM/data/intermediate/nemia_buff_aea.rds")
nemia_buff = st_transform(nemia_buff_aea, crs = 4326) 
aod_site_NE <- aod_site_sf[nemia_buff,]

# NEMIA site list
# site_list_NE <- c(aod_site_NE$Site_Name, "MVCO", "LISCO")
site_list_NE <- c(aod_site_NE$Site_Name)
# US site list
# to be done

@@

### fit the model 
time0 <- Sys.time()
system.time(d2 <- d[, by = obs, .(AOD_470nm = exp(predict(lm(log(aod) ~  log(exact_wv) + I((log(exact_wv))^2)), newdata = data.frame(exact_wv = 470))))])
Sys.time() - time0 # 6.3 hours 6/19

@@

lst_files <- list.files(path = "/data-coco/mcd19/fst/nemia/2018", pattern = "mcd19_T", full.names = T)
terra0 <- read.fst(lst_files[1], as.data.table = T)
# load lst data for 2018

read.lst <- function(sat = "terra"){
  if (sat != "terra") choose = "mcd19_T" else choose = "mcd19_A" # load terra by default
  lst_files <- list.files(path = "/data-coco/mcd19/fst/nemia/2018", pattern = choose, full.names = T)
  dt = rbindlist(lapply(lst_files, function(x)read.fst(x,as.data.table = T)))
  dt[,c("x","y", "inNEMIA"):=NULL]

  dt[, join_time:=overpass_time]
  setkey(dt, idLSTpair0, join_time)
  return(dt)
}
lst_terra <- read.lst()

# make sure both are UTC time 
# attr(aod20_NEMIA_idLST$stn_time, "tzone")
# attr(lst_terra$overpass_time, "tzone")

@@

vars0 <- c("overpass_index", "Optical_Depth_047", "AOD_Uncertainty", "Column_WV", "AOD_QA",  "RelAZ")
vars_new <- paste0(vars0,"_t")
setnames(aod_lst_terra, vars0, vars_new)
# set NA 
aod_lst_terra[within30min_t==0, c(vars_new):= NA]

@@

# time difference
aod_lst_aqua[, diff_time_min:= as.numeric(overpass_time - stn_time)/60]
vars_new <- paste0(vars0,"_a")
setnames(aod_lst_aqua, vars0, vars_new)
aod_lst_aqua[abs(diff_time_min)>30, c(vars_new):= NA]

# save
saveRDS(list(aod_lst_terra = aod_lst_terra, aod_lst_aqua=aod_lst_aqua), "~/Intermediate/AOD_data/190629_LSTjoinMCD19_t_a.rds")

@@

* Terra  
```{r}
# report
aod_lst_terra <- readRDS("~/Intermediate/AOD_data/190629_LSTjoinMCD19_t_a.rds")$aod_lst_terra

>>>>

---
title: "Import and process AODV3 Level2 AOD20 from Aeronet"
author: "Yang Liu"
date: "6/4/2019"
output:
  html_document:
    toc: true
---
```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = F, message=FALSE, warning=FALSE,
                      error = F, fig.width = 7, fig.height = 4.5)
```

Borrowed some code from `03_import_aeronet.R` on Jdrive  
Import and process the AOD20 V3 level 2 global Aeronet stations  
Interpolating to wavelength AOD 470nm

@@

```{r}
source("~/liuyanguu/CWV/Code/cwv_funcs.R")
source(here::here("Code", "funcs_for_plots.R"))

@@

aod_site_sf <- st_as_sf(site_locations_2019, coords = c("lon", "lat"), crs = 4326)
nemia_buff_aea <- readRDS("~/Jdrive/PM/Just_Lab/projects/ECHO_PM/data/intermediate/nemia_buff_aea.rds")
nemia_buff = st_transform(nemia_buff_aea, crs = 4326) 
aod_site_NE <- aod_site_sf[nemia_buff,]  # a sf object for NEMIA
saveRDS(aod_site_NE, here("Intermediate", "aod_site_NE"))
# NEMIA site list
# site_list_NE <- c(aod_site_NE$Site_Name, "MVCO", "LISCO")
site_list_NE <- c(aod_site_NE$Site_Name)
# US site list
# to be done

@@

## project to 470 nm

```{r, eval = F}
time0 <- Sys.time()
system.time(d2 <- d[, by = obs, .(AOD_470nm = exp(predict(lm(log(aod) ~  log(exact_wv) + I((log(exact_wv))^2)), newdata = data.frame(exact_wv = 470))))])
Sys.time() - time0 # 6.3 hours 6/19

@@

## this part obtain the binded NEMIA MCD19 data 
lst_files <- list.files(path = "/data-coco/mcd19/fst/nemia/2018", pattern = "mcd19_T", full.names = T)
terra0 <- read.fst(lst_files[1], as.data.table = T, columns = NULL)

# load lst data for 2018
read.lst <- function(sat = "terra", columns0 = NULL){
  if (sat != "terra") choose = "mcd19_T" else choose = "mcd19_A" # load terra by default
  lst_files <- list.files(path = "/data-coco/mcd19/fst/nemia/2018", pattern = choose, full.names = T)
  dt = rbindlist(lapply(lst_files, function(x)read.fst(x, as.data.table = T, columns  = columns0)))
  if(is.null(columns0)) dt[,c("x", "y", "inNEMIA"):=NULL]

  dt[, join_time:=overpass_time]
  setkey(dt, idLSTpair0, join_time)
  return(dt)
}
lst_terra <- read.lst()
print(object.size(lst_terra), unit = "GB") # 18 GB all the lst terra in 2018 (NEMIA, one year)
# make sure both are UTC time 
# attr(aod20_NEMIA_idLST$stn_time, "tzone")
# attr(lst_terra$overpass_time, "tzone")

@@

# vars0 <- c("overpass_index", "Optical_Depth_047", "AOD_Uncertainty", "Column_WV", "AOD_QA",  "RelAZ")
# vars_new <- paste0(vars0,"_t")
# setnames(aod_lst_terra, vars0, vars_new)
# set NA 
aod_lst_terra <- aod_lst_terra[within30min_t!=0,]

@@

# time difference
aod_lst_aqua[, diff_time_min:= as.numeric(overpass_time - stn_time)/60]
# vars_new <- paste0(vars0,"_a")
# setnames(aod_lst_aqua, vars0, vars_new)
aod_lst_aqua <- aod_lst_aqua[abs(diff_time_min)<=30,]

# save
saveRDS(list(aod_lst_terra = aod_lst_terra, aod_lst_aqua = aod_lst_aqua), "~/Intermediate/AOD_data/190629_LSTjoinMCD19_t_a.rds")

@@

* Terra

```{r}
# report
aod_lst_terra <- readRDS("~/Intermediate/AOD_data/190629_LSTjoinMCD19_t_a.rds")$aod_lst_terra
